Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2015-07-13 documentation/userguide.tex
Phase out the ability to have different source code. The user could still compile their own code and then use our job submission system, but they need to provide their own source code and makefile to do this.

This chapter describes the necessary steps you need to take to build your own problem setup,
and describes the underlying code that facilitates the job submission. If you are interested in
doing white dwarf mergers and want to use the default settings, read Section \ref{sec:standard_problems}.
If you are interested in setting up a different problem but using this software's job submission 
system, you can do so; read Section \ref{sec:non-standard_problems} for more information.

@@

If you want to build your own problem setup, you can do that too. The makefile and job submission 
requirements are the same as in Section \ref{sec:standard_problems}, but you will need to provide 
your own source files. They should all go in a \texttt{source/} subdirectory in your problem location.
At minimum, you'll need a \texttt{Prob\_3d.f90} file (or the equivalent for lower dimensions) and a 
probin file. The probin file can be empty, it just needs to be there because otherwise the helper 
routines will make a copy of the default probin file. To get a sense of how this is done, look at 
some of the existing test problems, in particular the \texttt{kelvin\_helmholtz} test. To tell the 
code that you want to compile this source code instead of the default code, make a file called 
\texttt{full\_source} and place it in the \texttt{source/} directory (you can just use \texttt{touch}
to create an empty file). Then follow the rest of the instructions as normal, starting with the 
compile step.

The only source code that will be built from the default location is \texttt{sum\_integrated\_quantities.cpp},
which controls the diagnostic output. Our version is a bit more extensive than what comes in CASTRO
by default, so we include this in every build.

>>>>

This chapter describes the necessary steps you need to take to build your own problem setup,
and describes the underlying code that facilitates the job submission. If you are interested in
doing white dwarf mergers and want to use the default source code, read Section \ref{sec:standard_problems}.
If you are interested in setting up a different problem but using this software's job submission 
system, you can do so; Section \ref{sec:non-standard_problems} gives some advice on that.

@@

If you want to build your own problem setup, you can do that too. The job submission 
requirements are the same as in Section \ref{sec:standard_problems}, but you will need to provide 
your own source files and makefile. They can go in the \texttt{compile/} subdirectory in your problem location.
At minimum, you'll need a \texttt{Prob\_3d.f90} file (or the equivalent for lower dimensions) and
corresponding inputs and probin files. The problems in \texttt{tests/castro} are similar to this;
they are ultimately building using the source code in the CASTRO test suite, but using a
\texttt{run\_test.sh} that is very similar to the one used for merger problems.
